%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Senior Software Engineer} % Job title
    {Assigncorp Canada} % Organization
    {Toronto, Canada} % Location
    {Nov 2020 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed deployment architechture and migration of test case management system (TestRail) from datacenter to GCP.}
        \item {Wrote bash scripts to deploy TestRail, MariaDB and Cassandra docker containers and to backup and restore data on a daily basis in GCE (Google Compute Instance).}
        \item {Implemented DR (Disaster Recovery) for Kubernetes cluster resources and persistent volumes using Velero. }
        \item {POC - implemented cloud native cluster-level Kubernetes storage (Rook/Ceph) operator for block and file systems storage in GKE (Google Kubernetes Engine) using HELM charts and Terraform scripts.}
        \item {POC - IaC using Terraform implemented cloud native registry (Harbor) in GKE to push and pull helm charts and docker images using OCI skopeo.}
        \item {POC - implementation of cloud native CI/CD, defined Tekton tasks, task run, pipeline, pipeline run, and used kaniko to build and push images to Harbor registry in GKE.}
        \item {Replaced ccache with sccache to build Android ASOP that enhanced build cache and resulted in faster build times.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior Software Engineer} % Job title
    {Noetic Information Systems Inc.} % Organization
    {Pleasanton, California} % Location
    {July 2019 - December 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        % \item {Designed and developed an overall service architecture Settlement service with the micro-services architecture.}
        % \item {Implemented several API microservices for Payment, Collection and Loan Management services in Java 8, Groovy, RabbitMQ, MySql.}
        % \item {Wrote a POC with LocalStack and showcased the team how it increased developer velocity by 60\% and reduced AWS costs by 40\%.}
        % \item {Wrote Swagger documentation for all REST APIs.}
        % \item {Emphasis on software quality and exercise TDD using Junit, Mockito, Spock, SonarQube, Jacoco. }
        % \item {Participate and contribute in design and code reviews.}
        \item {Implemented API microservices for Payment, Collection, and Loan Management services in Java 8, Groovy, RabbitMQ, MySql.}
        \item {Wrote POC with LocalStack and showcased team how it increased developer velocity by 60\% and reduced AWS costs by 40%.}
        \item {Wrote Swagger documentation for all REST APIs.}
        \item {Acheived software quality and exercised TDD using Junit, Mockito, Spock, SonarQube, Jacoco.}
        \item {Lead and contributed to design and code reviews.}}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior Software Engineer} % Job title
    {EllieMae Inc.} % Organization
    {Pleasanton, California} % Location
    {March 2015 - July 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed scalable REST microservices, HA, fault-tolerant Activities stream producers and consumers using AWS, Java 11, Kafka, PostgreSQL.}
        \item {Implemented automated CI/CD pipelines in Jenkins as JenkinsFile, Docker, AWS ECS.}
        \item {Participated and contributed in architecture for Document Platform Services using microservices architecture.}
        \item {Developed REST APIs for Document Platform Services using Java 8/11, SpringBoot, Kafka, PostgreSQL, and MongoDB.}
        \item {Implemented Structured Logging using MDC, ELK, Filebeat, and CloudWatch.}
        \item {Implemented in-memory HTML to PDF conversion using Qt Framework written in C++.}
        \item {TDD using Junit, Mockito, Spock, and publish Jacoco reports to SonarQube targeted at 80\% coverage.}
        \item {Participate and contribute in design and code reviews as part of the Scrum process.}
        \item {Create, update design and architecture documentation using draw.io in Confluence.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior Software Engineer)} % Job title
    {McKesson Corporation} % Organization
    {Emeryville, California} % Location
    {March. 2009 - March. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed and Implemented CCDA, HL7 message parsers using C\#, LINQ.}
        \item {Designed and Developed RESTful APIs to exchange XDS,XCA messages and retrieve blobs from Azure table storage using C\#.}
        \item {Modify and maintain existing SOA web services leveraging MassTransit event bus backed up with RabbitMQ using C\# per business requirements.}
         \item {Exercised TDD using Nunit, Moq and WatiN frameworks. }
        \item {Participate and contribute in design and code reviews.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Developer} % Job title
    {United BioSource} % Organization
    {San Francisco, California} % Location
    {April 2007 - March 2009} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed DHRS Engine using C\# 2.0 for Dynamic Hierarchical Randomization that enables treatment assignment to a patient in Clinical Trials.} 
        \item {Designed and Implemented Stratification Engine using C\# 2.0 to stratify patients. }
        \item {Designed and implemented IVR and Web systems using C\#, SQL Server.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior Software Consultant} % Job title
    {UBICS Inc.} % Organization
    {Pittsburgh, Pennsylvania} % Location
    {July 2006 - March 2007} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      	\item {Developed DAL using C\# 2.0  to interface with IBM DB2, MySQL databases and wrote Stored Procedures.}
      	\item {Designed and developed a Windows service for scheduled delivery reports.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior Software Consultant} % Job title
    {Softnet Solutions Inc.} % Organization
    {Manhattan, New York} % Location
    {April 2006 - June 2006} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item { Designed and developed Widgets component according to W3C standards using C\#. }
        \item {Developed multithreaded Graphics engine to render widgets and Playtime objects using C\#. }
      \end{cvitems}
      %\begin{cvsubentries}
      %  \cvsubentry{}{KNOX(Solution for Enterprise Mobile Security) Penetration Testing}{Sep. 2013}{}
      %  \cvsubentry{}{Smart TV Penetration Testing}{Mar. 2011 - Oct. 2011}{}
      %\end{cvsubentries}
    }

%---------------------------------------------------------


%---------------------------------------------------------
\cventry
{Senior Software Engineer} % Job title
{K. Systems} % Organization
{Pohang, South Korea} % Location
{August 2005 - February 2006} % Date(s)
{
	\begin{cvitems} % Description(s) of tasks/responsibilities
		\item {Wrote Technical Design Documents and functional specs for industrial automation systems. }
		\item {Designed and developed KMedia Encoder Server DCOM Component and Laser Measurement System a multi-threaded communication component that interacts with a hardware unit using C++. }
	\end{cvitems}
	%\begin{cvsubentries}
	%  \cvsubentry{}{KNOX(Solution for Enterprise Mobile Security) Penetration Testing}{Sep. 2013}{}
	%  \cvsubentry{}{Smart TV Penetration Testing}{Mar. 2011 - Oct. 2011}{}
	%\end{cvsubentries}
}

%---------------------------------------------------------


%---------------------------------------------------------
\cventry
{Senior Software Engineer} % Job title
{iSOFT} % Organization
{Chennai, India} % Location
{August 2004 - July 2005} % Date(s)
{
	\begin{cvitems} % Description(s) of tasks/responsibilities
		\item {Wrote Technical Design Documents, Involved in Analysis of System Design and functional specification. }
		\item {Supported legacy systems using VC++ and integrated with other vendor systems.}
		\item {Design and implemented GP2GP new Enhancement Feature that is EHR (Electronic Health Record) transfer of records from primary GP systems to destination GP systems, which contains all the necessary details of the transferred patients using C\#}
	\end{cvitems}
	%\begin{cvsubentries}
	%  \cvsubentry{}{KNOX(Solution for Enterprise Mobile Security) Penetration Testing}{Sep. 2013}{}
	%  \cvsubentry{}{Smart TV Penetration Testing}{Mar. 2011 - Oct. 2011}{}
	%\end{cvsubentries}
}


%---------------------------------------------------------
\cventry
{Senior Software Engineer} % Job title
{Digital Alarm Technologies} % Organization
{Chennai, India} % Location
{April 2000 - July 2004} % Date(s)
{
	\begin{cvitems} % Description(s) of tasks/responsibilities
		\item {Developed access control systems and building automation systems designed as n-tier distributed systems in Windows environment using COM/DCOM.}
		\item {Architected, designed, prototyped and implemented COM/DCOM interfaces and multi-threaded components in VC++ using ATL/STL and MFC based on the protocol that interfaces with hardware units. }
		\item {Developed the multi-threaded Event Server component that was loosely designed on OLE Process Control (OPC) industry standard. }
	\end{cvitems}
	%\begin{cvsubentries}
	%  \cvsubentry{}{KNOX(Solution for Enterprise Mobile Security) Penetration Testing}{Sep. 2013}{}
	%  \cvsubentry{}{Smart TV Penetration Testing}{Mar. 2011 - Oct. 2011}{}
	%\end{cvsubentries}
}

%---------------------------------------------------------

%---------------------------------------------------------
\end{cventries}
